Automatic Hadith Graphs using Arabic Morphological Analysis

### 2011-06-02 trunk/tex/hadith.ijcnlp.tex
added tables

\begin{table}[tb]
%\centering
%\resizebox{.9\columnwidth}{!}{
\begin{tabular} {p{6cm}}
\begin{Verbatim}[fontsize=\relsize{-2},
frame=topline,framesep=4mm,label=\fbox{MergeChains algorithm},
commandchars=\\\{\}, codes={\catcode`$=3\catcode`_=8}]
Merge(Chain $C$[])
  Chain $C_c$[]=\{\}
  foreach Chain $c_1$ in $C$ 
    $C_c = C_c \cup c_1$
    foreach Narrator $n_1$ in $c_1$
      foreach Chain $c_2$ in $C-C_c$
        foreach narrator $n_2$ in $c_2$

    \}
  \}
\end{Verbatim}
\end{tabular}
%}
\label{a:merge}
\end{table}

@@

\subsection{Use of the POR graph}

inconsistency check 
consistency checks
annotate with information extracted from biographies
what if analysis

@@

\begin{table}[bt]
\centering
\caption{Results of the hadith case study with Sarf.}
%\begin{tabular}{|p{1.5cm}||c|c||c|c||c|c|} \hline
\resizebox{1.1\columnwidth}{!}{
\begin{tabular}{lcp{.2cm}cp{.2cm}c} %\cline{2-10}
 &  AlKafi & & AlIstibsar & &IbnHanbal \\ \cline{1-6}
Word count  &98,943 & & 103,835 & & 20,354 \\ 
 Names       & 12,060  & & 14,613& & 3,013\\
%Names/Narrator & 1.97 & & 1.84& & 1.25 \\
Narrators  & 2,623 & & 5,767& & 1,755 \\ 
%Narrators/Chain  & 4.84 & & 4.76 & &4.05 \\
Chains  & 542 &  & 1,211& & 433 \\ 
Ignored names  & 6,400 &  & 3,348 & & 642 \\ \hline
Segmentation accuracy  & 96\%& & 96\%& & 92\%\\ 
Chain accuracy & 99\%&  & 99\%& & 97\% \\ 
%Narrator accuracy  & & & & &  & & & \\ 
Narrator accuracy  & 91\%& & 90\% & & 90\% \\ \hline
%Name false positives  & 7\%&  & 4\% & & 4\% \\ \hline
Running time (secs.)& 1.32 & & 1.31 & & .096\\ \hline 
\end{tabular}
}
\normalsize
\label{t:hadithresallresults}
\end{table}

>>>>

\begin{table}[tb]
%\centering
%\resizebox{.9\columnwidth}{!}{
\begin{tabular} {p{6cm}}
\begin{Verbatim}[fontsize=\relsize{-2},
frame=topline,framesep=4mm,label=\fbox{MergeChains algorithm},
commandchars=\\\{\}, codes={\catcode`$=3\catcode`_=8}]
Merge(Chain $C$[])
  Chain $C_c$[]=\{\}
  foreach Chain $c_1$ in $C$ 
    $C_c = C_c \cup c_1$
    foreach Chain $c_2$ in $C-C_c$
      foreach Narrator $n_1$ in $c_1$
        start = max( $n_1$.index - radius, 0)
        end = min($n_1$.index + radius, $n_2$.size)
        $n_2$ = $c_2$[start]
        while (true)
            if (Distance($n_1$, $n_2$) < $\theta$)
                mergeNodes($n_1$, $n_2$)
            if ($n_2$ = $c_2$[end])
                    break
            $n_2$ = $c_2$.next($n_2$)        
\end{Verbatim}
\end{tabular}
%}
\label{a:merge}
\end{table}

@@

\subsection{Use of the POR graph}
inconsistency check 
consistency checks
annotate with information extracted from biographies
what if analysis

@@

%\begin{table}[bt]
%\centering
%\caption{Results of the hadith case study with Sarf.}
%%\begin{tabular}{|p{1.5cm}||c|c||c|c||c|c|} \hline
%\resizebox{1.1\columnwidth}{!}{
%\begin{tabular}{lcp{.2cm}cp{.2cm}c} %\cline{2-10}
% &  AlKafi & & AlIstibsar & &IbnHanbal \\ \cline{1-6}
%Word count  &98,943 & & 103,835 & & 20,354 \\ 
% Names       & 12,060  & & 14,613& & 3,013\\
%%Names/Narrator & 1.97 & & 1.84& & 1.25 \\
%Narrators  & 2,623 & & 5,767& & 1,755 \\ 
%%Narrators/Chain  & 4.84 & & 4.76 & &4.05 \\
%Chains  & 542 &  & 1,211& & 433 \\ 
%Ignored names  & 6,400 &  & 3,348 & & 642 \\ \hline
%Segmentation accuracy  & 96\%& & 96\%& & 92\%\\ 
%Chain accuracy & 99\%&  & 99\%& & 97\% \\ 
%%Narrator accuracy  & & & & &  & & & \\ 
%Narrator accuracy  & 91\%& & 90\% & & 90\% \\ \hline
%%Name false positives  & 7\%&  & 4\% & & 4\% \\ \hline
%Running time (secs.)& 1.32 & & 1.31 & & .096\\ \hline 
%\end{tabular}
%}
%\normalsize
%\label{t:hadithresallresults}
%\end{table}
%

\begin{table*}[bt]                                     
\centering                                            
\caption{Results comparing between NaGEMA and iTree.}
\resizebox{2.1\columnwidth}{!}{
\begin{tabular}{p{2.1cm}lp{.1cm}cccp{.1cm}cccp{.1cm}ccc}
%\multicolumn{13}{c}{NaGEMA with all refinements} \\ \cline{3-13}
& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{NaGEMA }&musnad & & 1.000 & 1.000 & 1.000 & & 0.993 & 0.990 & 0.991 & & 0.999 & 0.998 & 0.999 \\
&kafi & & 1.000 & 0.920 & 0.958 & & 0.937 & 0.970 & 0.953 & & 0.993 & 0.988 & 0.990 \\
&istibsar & & 1.000 & 0.973 & 0.986 & & 0.980 & 0.950 & 0.965 & & 0.996 & 0.998 & 0.997 \\ \cline{2-14}
& & & 1.000 & 0.964 & 0.982 & & 0.970 & 0.970 & 0.970 & & 0.996 & 0.995 & 0.995 \\ \hline \hline
%& & &  &  &  & &  &  &  & &  &  & \\
%&\multicolumn{13}{c}{iTree} \\ \cline{3-13}
& & & \multicolumn{3}{c}{accept as hadith} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{iTree} &musnad & & 1.000 & NA & 1.000 & & 0.997 & 0.977 & 0.987 & & 0.998 & 1.000 & 0.999  \\
&kafi & & 0.043 & NA & 0.083 & & 1.000 & 0.313 & 0.476 & & 1.000 & 1.000 & 1.000 \\
&istibsar & & 0.028 & NA & 0.054 & & 0.875 & 0.583 & 0.700 & & 1.000 & 1.000 & 1.000 \\ \cline{2-14}
& & & 0.357 & NA & 0.379 & & 0.957 & 0.624 & 0.721 & & 0.999 & 1.000 & 1.000 \\ 
 \end{tabular}                 
}                             
\normalsize                   
\label{t:hadithresults} 
\end{table*}

\begin{table*}[bt]                                     
\centering                                            
\caption{Results without punctuation and without learning. }
\resizebox{2.1\columnwidth}{!}{
\begin{tabular}{p{2.1cm}lp{.1cm}cccp{.1cm}cccp{.1cm}ccc}
& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{no punctuation} 
& musnad  & & 1.000 & 1.000 & 1.000 & & 0.982 & 0.955 & 0.968 & & 1.000 & 0.998 & 0.999 \\ 
& kafi & & 1.000 & 0.793 & 0.885 & & 0.944 & 0.967 & 0.955 & & 0.996 & 0.938 & 0.966 \\
& istibsar & & 1.000 & 1.000 & 1.000 & & 0.980 & 0.931 & 0.955 & & 0.994 & 0.985 & 0.990 \\  \cline{2-14}
& &  & 1.000 & 0.931 & 0.962 & & 0.969 & 0.951 & 0.960 & & 0.997 & 0.974 & 0.985 \\ \hline \hline
%& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
%& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{no learning}
& musnad & & 1.000 & 1.000 & 1.000 & & 0.894 & 0.985 & 0.937 & & 0.995 & 1.000 & 0.998\\
& kafi & & 1.000 & 0.920 & 0.958 & & 0.937 & 0.970 & 0.953 & & 0.993 & 0.991 & 0.992\\
& istibsar & & 1.000 & 0.973 & 0.986 & & 0.977 & 0.950 & 0.963 & & 0.996 & 0.998 & 0.997\\ \cline{2-14}
 & &  & 1.000 & 0.964 & 0.982 & & 0.936 & 0.968 & 0.951 & & 0.995 & 0.996 & 0.995 \\
 \end{tabular}                 
}                             
\normalsize                   
\label{t:nopunctlearnresults} 
\end{table*}
